Supplemental Materials

### 2021-07-20 supplement/supplement-main.Rmd
reverse order of x-axis on fig 6, correct scale labels

recode_nodes2 <- function(x){
  recode(x,
         "diseaseRare" = "Disease Rarity",
         "diseaseSevere" = "Disease Severity",
         "hb" = "Holistic Balance",
         "infantImmLimCap" = "IIS: Lim. Capacity",
         "infantImmWeak" = "IIS: Weakness",
         "medSkept" = "Med. Skepticism",
         "nat" = "Naturalism",
         "overpar" = "Parental Protectiveness",
         "parentExpert" = "Parental Expertise",
         "vaccDanger" = "Vaccine Danger",
         "vaccEff" = "Vaccine Eff.",
         "vaccIntent" = "Vaccination Intentions",
         "vaccStrain" = "IIS: Vaccines Strain",
         "vaccTox" = "Vaccines Toxicity")}

@@

s4_scale_order <- combined %>% 
  drop_na(scale) %>% 
  mutate(posttest = rescale_beta(posttest, -3, 3), 
         pretest = rescale_beta(pretest, -3, 3)) %>% 
  mutate(diff = posttest-pretest) %>% 
  mutate(scale = recode_nodes2(scale)) %>% 
  group_by(vacc_news, scale) %>%
  summarize(M = mean(diff, na.rm=TRUE)) %>%
  ungroup() %>%
  group_by(scale) %>%
  summarize(diff_diff = mean(M, na.rm = T)) %>%
  ungroup() %>%
  arrange(diff_diff) %>% # ascending because news exposure is expected to increase vaccine intentions
  mutate(order = 1:nrow(.))

>>>>

recode_nodes2 <- function(x){
  recode(x,
         "diseaseRare" = "Disease Rarity",
         "diseaseSevere" = "Disease Severity",
         "hb" = "Holistic Balance",
         "infantImmLimCap" = "IIS: Lim. Capacity",
         "infantImmWeak" = "IIS: Weakness",
         "medSkept" = "Med. Skepticism",
         "nat" = "Naturalism",
         "overpar" = "Parental Protectiveness",
         "parentExpert" = "Parental Expertise",
         "vaccDanger" = "Vaccine Danger",
         "vaccEff" = "Vaccine Effectiveness",
         "vaccIntent" = "Vaccination Intentions",
         "vaccStrain" = "IIS: Vaccines Strain",
         "vaccTox" = "Vaccine Toxicity")}

@@

s4_scale_order <- combined %>% 
  drop_na(scale) %>% 
  mutate(posttest = rescale_beta(posttest, -3, 3), 
         pretest = rescale_beta(pretest, -3, 3)) %>% 
  mutate(diff = posttest-pretest) %>% 
  mutate(scale = recode_nodes2(scale)) %>% 
  group_by(vacc_news, scale) %>%
  summarize(M = mean(diff, na.rm=TRUE)) %>%
  ungroup() %>%
  group_by(scale) %>%
  summarize(diff_diff = mean(M, na.rm = T)) %>%
  ungroup() %>%
  arrange(desc(diff_diff)) %>% # ascending because news exposure is expected to increase vaccine intentions
  mutate(order = 1:nrow(.))
